problem years

### 2024-08-14 src/problem_years.Rmd
sum corrected

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>% # for multiple pc  
  ungroup() %>% 
  complete(oa11cd, year) %>% 
  filter(!is.na(oa11cd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/OA/morani_oa_1.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```

>>>>

```{r}
df <- df.corrected %>% 
  mutate(year = as.integer(as.character(year))) %>% 
  filter(year > 1995 & year < 2013) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = sum(n)) %>% # **********ATTENTION*********    
  ungroup() %>% 
  complete(oa11cd, year) %>% 
  filter(!is.na(oa11cd)) %>% # drop c. 10 - 200 per year, which are not assigned to a LAD
  replace(is.na(.), 0) 
```

@@

```{r}
path.out <- paste0(path, "/outputs/lisa/corrected/OA/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  #kable() %>% 
  write_csv(path.out)
```
